### 2022-02-11 abstract.tex
abstract

\begin{abstract}
    In this work, we present \acs*{CLEAVE}, a novel, completely software-based framework for repeatable and scalable experimentation in \acfp*{NCS}.
    While these systems have long been a subject of both theoretical and experimental research, their inter-domain nature  has led to a wide number of task-specific approaches to research, and little work has been devoted to generalizable, repeatable, and scalable experimentation.
    We aim to tackle this gap in knowledge through an approach based on the emulation of physical plants which communicate over a real network with controllers implemented in software.
    \acs*{CLEAVE} is furthermore designed and built for the edge, using Python3 and with full compatibility with industry-standard containerization solutions.
    Although designed for single-loop emulations, the flexibility afforded by the aformentioned characteristics allow our framework to be adaptated to and employed in a multitude of more complex scenarios.

>>>>

\begin{abstract}
    In this work, we present \acs*{CLEAVE}, a novel, completely software based framework for repeatable and scalable experimentation in \acfp*{NCS}.
    While these systems have long been a subject of both theoretical and experimental research, their inter-domain nature  has led to a wide number of task-specific approaches to research, and little work has been devoted to generalizable, repeatable, and scalable experimentation.
    We aim to tackle this gap in knowledge through an approach based on the emulation of physical plants which communicate over a real network with controllers implemented in software.
    \acs*{CLEAVE} is furthermore designed and built for the edge, using Python3 and with full compatibility with industry-standard containerization solutions.
    Although designed for single-loop emulations, the flexibility afforded by the aformentioned characteristics allow our framework to be adaptated to and employed in a multitude of more complex scenarios.
